Boutiques: a flexible framework for automated application integration in computing platforms

### 2016-11-01 paper.tex
Added parallelization to the application table

\usepackage{minted} % Used for JSON highlighting
\usepackage{pdfcomment} % Used for notes and todos
\usepackage[margin=1in]{geometry} % Increases margins
\usepackage{lscape} % Used to put a section in landscape mode
\usepackage[table]{xcolor} % Color definitions
\usepackage{algorithm} % Algorithm float
\usepackage{algpseudocode} % Algorithmic environment

@@

Algorithm~\ref{algo:command-line} shows how the application command
line is constructed from the application manifest and values entered
by the user. It substitutes all the value keys in the command line,
output path templates and configuration files, and writes the
configuration files.

\begin{algorithm}[htb]
\caption{Command-line construction}
\label{algo:command-line}
\begin{algorithmic}
  \State \Comment{Substitute input value keys in output path templates, configuration files and command line.}
  \For{\texttt{input} in \texttt{inputs}}
  \If{\texttt{input} has a \texttt{value-key}}
  \For{\texttt{output} in \texttt{outputs}}
  \State \texttt{stripped\_value} = \texttt{input\_value}
  \If{\texttt{input} type is \texttt{File}}
  \State In \texttt{stripped\_value}, remove  all elements in \texttt{path-template-stripped-extensions}.
  \EndIf
  \State In \texttt{path-template}, replace all occurrences of \texttt{value-key} by \texttt{stripped\_value}.
  \If{\texttt{output} has a \texttt{file-template}}
  \State In any line of \texttt{file-template}, replace all occurrences of \texttt{value-key} by \texttt{stripped\_value}.
  \EndIf
  \EndFor
  \State Prepend \texttt{command-line-flag} and \texttt{command-line-flag-separator} to \texttt{input\_value}.
  \State In \texttt{command-line}, replace all occurrences of \texttt{value-key} by \texttt{input\_value}.
  \EndIf
  \EndFor

@@

Table~\ref{table:applications} summarizes the applications described
with Boutiques and the main features used.
\begin{landscape}
  \begin{table}
  \rowcolors{2}{gray!25}{white}
  \begin{tabular}{l|ccc|ccccccc|cc}
    Application               &\multicolumn{3}{c|}{Containers} & \multicolumn{7}{c|}{Input/Output properties}                         & \multicolumn{2}{c}{Other properties}  \\
                              &Docker              & Singularity & Rootfs  & Dependencies      &Groups             & Lists             & Optional          &Default            & Enum              & Min/max           & Config. file & Env vars     \\
    \hline
    Niak pre-processing       &\cellcolor{gray!75} &            &         &                   &\cellcolor{gray!75}&                   &\cellcolor{gray!75}&\cellcolor{gray!75}&\cellcolor{gray!75}&\cellcolor{gray!75}&              &\cellcolor{gray!75}\\
    ICA AROMA                 &\cellcolor{gray!75} &            &         &\cellcolor{gray!75}&\cellcolor{gray!75}&                   &\cellcolor{gray!75}&\cellcolor{gray!75}&\cellcolor{gray!75}&\cellcolor{gray!75}&              &\\
    FSL tools &&&&&&&&&&&&\\
    \multicolumn{1}{r|}{anat} &                    &            &         &\cellcolor{gray!75}&\cellcolor{gray!75}&                   &\cellcolor{gray!75}&\cellcolor{gray!75}&\cellcolor{gray!75}&\cellcolor{gray!75}&              &\\
    \multicolumn{1}{r|}{bet}  &                    &            &         &\cellcolor{gray!75}&\cellcolor{gray!75}&\cellcolor{gray!75}&\cellcolor{gray!75}&                   &                   &\cellcolor{gray!75}&              &\\      
    \multicolumn{1}{r|}{fast} &                    &            &         &\cellcolor{gray!75}&                   &                   &\cellcolor{gray!75}&\cellcolor{gray!75}&\cellcolor{gray!75}&\cellcolor{gray!75}&              &\\
    \multicolumn{1}{r|}{first}&                    &            &         &                   &                   &\cellcolor{gray!75}&\cellcolor{gray!75}&\cellcolor{gray!75}&                   &                   &              &\\
    FSL Nipype interfaces     \\
    HCP PreFreesurfer         &\cellcolor{gray!75} &            &         &                   &                   &                   &                   &                   &                   &                   &              &\\
    MSSEG MICCAI pipelines    \\
    PETSEG MICCAI pipelines   \\
\end{tabular}
\caption{Applications available in Boutiques with manifest features used.}
\label{table:applications}
  \end{table}
  \end{landscape}

>>>>

\usepackage{minted} % Used for JSON highlighting
\usepackage{pdfcomment} % Used for notes and todos
\usepackage[margin=1in]{geometry} % Increases margins
\usepackage[table]{xcolor} % Color definitions
\usepackage{algorithm} % Algorithm float
\usepackage{algpseudocode} % Algorithmic environment

@@

Algorithm~\ref{algo:command-line} shows how the application command
line is constructed from the application manifest and values entered
by the user. It substitutes all the value keys in the command line,
output path templates and configuration files, and writes the
configuration files.
\begin{algorithm}[h!]
\caption{Command-line construction}
\label{algo:command-line}
\begin{algorithmic}
  \State \Comment{Substitute input value keys in output path templates, configuration files and command line.}
  \For{\texttt{input} in \texttt{inputs}}
  \If{\texttt{input} has a \texttt{value-key}}
  \For{\texttt{output} in \texttt{outputs}}
  \State \texttt{stripped\_value} = \texttt{input\_value}
  \If{\texttt{input} type is \texttt{File}}
  \State In \texttt{stripped\_value}, remove  all elements in \texttt{path-template-stripped-extensions}.
  \EndIf
  \State In \texttt{path-template}, replace all occurrences of \texttt{value-key} by \texttt{stripped\_value}.
  \If{\texttt{output} has a \texttt{file-template}}
  \State In any line of \texttt{file-template}, replace all occurrences of \texttt{value-key} by \texttt{stripped\_value}.
  \EndIf
  \EndFor
  \State Prepend \texttt{command-line-flag} and \texttt{command-line-flag-separator} to \texttt{input\_value}.
  \State In \texttt{command-line}, replace all occurrences of \texttt{value-key} by \texttt{input\_value}.
  \EndIf
  \EndFor

@@

Table~\ref{table:applications} summarizes the applications described
with Boutiques and the main features used.

\begin{table}
  \begin{tabular}{l|ccccccc}
    \rowcolor[gray]{0.9}
    Application               &\multicolumn{7}{c}{Input/Output properties} \\
    \rowcolor[gray]{0.9}
    & Dependencies      &Groups             & Lists             & Optional          &Default            & Enum              & Min/max\\

    \hline
    Niak pre-processing       &                   &\cellcolor{gray!75}&\cellcolor{gray!75}&\cellcolor{gray!75}&\cellcolor{gray!75}&\\
    ICA AROMA                 &\cellcolor{gray!75}&\cellcolor{gray!75}&                   &\cellcolor{gray!75}&\cellcolor{gray!75}&\cellcolor{gray!75}&\cellcolor{gray!75}\\
    FSL tools &&&&&&\\
    \multicolumn{1}{r|}{anat} &\cellcolor{gray!75}&\cellcolor{gray!75}&                   &\cellcolor{gray!75}&\cellcolor{gray!75}&\cellcolor{gray!75}&\cellcolor{gray!75}\\
    \multicolumn{1}{r|}{bet}  &\cellcolor{gray!75}&\cellcolor{gray!75}&\cellcolor{gray!75}&\cellcolor{gray!75}&                   &                   &\cellcolor{gray!75}\\      
    \multicolumn{1}{r|}{fast} &\cellcolor{gray!75}&                   &                   &\cellcolor{gray!75}&\cellcolor{gray!75}&\cellcolor{gray!75}&\cellcolor{gray!75}\\
    \multicolumn{1}{r|}{first}&                   &                   &\cellcolor{gray!75}&\cellcolor{gray!75}&\cellcolor{gray!75}&                   &                   \\
    FSL Nipype interfaces     \\
    HCP PreFreesurfer         &                   &                   &                   &                   &                   &                   &                   \\
    MSSEG MICCAI pipelines    \\
    PETSEG MICCAI pipelines   \\
    \end{tabular}
  \vspace*{0.5cm}
  \begin{tabular}{l|ccc|ccc}
    \hline
    \rowcolor[gray]{0.9}
    Application               &\multicolumn{3}{c|}{Containers} &  \multicolumn{3}{c}{Other properties}  \\
    \rowcolor[gray]{0.9}
    &Docker              & Singularity & Rootfs  & Config. file & Env vars  & Parallelization   \\
    \hline
    Niak pre-processing       &\cellcolor{gray!75} &            &         &              &\cellcolor{gray!75}&\cellcolor{gray!75}\\
    ICA AROMA                 &\cellcolor{gray!75} &            &         &              &&\\
    FSL tools &&&&&\\
    \multicolumn{1}{r|}{anat} &                    &            &         &              &&\\
    \multicolumn{1}{r|}{bet}  &                    &            &         &              &&\\
    \multicolumn{1}{r|}{fast} &                    &            &         &              &&\\
    \multicolumn{1}{r|}{first}&                    &            &         &              &&\\
    FSL Nipype interfaces     \\
    HCP PreFreesurfer         &\cellcolor{gray!75} &            &         &             &&\\
    MSSEG MICCAI pipelines    \\
    PETSEG MICCAI pipelines   \\
  \end{tabular} 
  \caption{Applications available in Boutiques with manifest features used.}
  \label{table:applications}
\end{table}
